Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Cite Stephan's thesis

In all but three cases, the Markov chains then give reliable results. But when
we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
strong correlations appear again. As a final solution, we then use importance
sampling with the initial proposal function determined by a fit of a Gaussian
mixture to the MCMC samples within the variational Bayes approximation. As the
posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
components are needed; i.e., 3 components proved optimal by the variational
approximation to the model evidence.

In the most challenging run with 62 parameters, we obtain a relative effective
sample size of only 0.038\%. We want to have enough independent samples $N$ such
that the 68\% region is determined with a relative precision of about 1\%. As a
rule of thumb, we consider the ``relative error of the error'' given by
$1/\sqrt{2 N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute
$1.1\cdot10^6$ importance samples such that $N \approx 3500$ and the estimated
relative error of the error is 1.2\% and thus good enough for our purposes.

>>>>

In all but three cases, the Markov chains then give reliable
results. But when we analyze scenarios with $\wilson{S,P} \ne 0$ and
all experimental constraints, strong correlations appear again. As a
final solution, we then use importance sampling with the initial
proposal function determined by a fit of a Gaussian mixture to the
MCMC samples within the variational Bayes
approximation~\cite{Jahn:2015}. As the posterior is unimodal and
closely resembles a Gaussian, only a few Gaussian components are
needed; i.e., 3 components proved optimal by the variational
approximation to the model evidence.

In the most challenging run with 62 parameters, we obtain a relative
effective sample size of only 0.038\%. We want to have enough
independent samples $N$ such that the 68\% region is determined with a
relative precision of about 1\%. As a rule of thumb, we consider the
``relative error of the error'' given by $1/\sqrt{2
  N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute a
total of $1.1\cdot10^6$ importance samples, update the proposal after
every $10^5$ samples, and combine all samples~\cite{Jahn:2015} such
that $N \approx 3500$ and the estimated relative error of the error is
1.2\% and thus good enough for our purposes.
